---
title: "Zillow Real Estate Data By Zip Code (USA)" 
output:
  ioslides_presentation:
    widescreen: true
date: Use the arrows on your keyboard to change slides 
outertheme: sidebar
runtime: shiny
---

```{r setup, include=FALSE ,echo=FALSE}
library(flexdashboard)
source("ZillowFormulas.R")
library(DT)
library(leaflet)
library(reticulate)
options(scipen=999)
```


*** 
**The data is grouped by the Zip code (one point per Zip).** <br/> <br/>
**This data is published by the Zillow Group and is updated and made publicly available [here](https://www.zillow.com/research/data/), where you can also find definitions for all of the variables. <br/> <br/> [Click here](https://www.zillow.com/research/about-us/) to learn more about Zillow Research** <br/> <br/>

**Select a state at the beginning and set it as the desired value for the rest of the presentation.** <br/> <br/>

**Made by [Riccardo Esclapon](https://www.linkedin.com/in/esclaponriccardo/) in R Shiny. ** <br/> <br/>

**Not affilitated with Zillow Group in any way. **


[Zillow Research](https://www.zillow.com/research/data/)
-----------------------------------------------------------------------

```{r,echo=FALSE, warning=F}
selectInput("stateFilter", "State", choices = c("NO FILTER",unique(data$State)), multiple=F, selectize=TRUE, selected = "NY" )
```


```{r,echo=FALSE}
renderLeaflet({
  data %>% stateSelect(stateFilter= input$stateFilter) %>% mapPres()
  })
```

Scatterplot 
-----------------------------------------------------------------------

```{r,echo=FALSE}
renderPlotly({
  data %>% stateSelect(stateFilter= input$stateFilter) %>% plotScatter()
})
```

Current state selection:
```{r, echo=F}
renderText({
  input$stateFilter
})
```

3d Chart
-----------------------------------------------------------------------

```{r,echo=FALSE}
renderPlotly({
  data %>% stateSelect(stateFilter= input$stateFilter) %>% plot3d() 
})
```

Current state selection:
```{r, echo=F}
renderText({
  input$stateFilter
})
```

Satellite Map
-----------------------------------------------------------------------

```{r,echo=FALSE}
renderLeaflet({
  data %>% stateSelect(stateFilter= input$stateFilter) %>% mapSat()
  })
```

Current state selection:
```{r, echo=F}
renderText({
  input$stateFilter
})
```

R Markdown Document
-----------------------------------------------------------------------

```{r,echo=T}
print('This code is written in R')
```

<br/> <br/>

```{python, echo=T}
print('This code is written in Python!')
```

<br/>

Current state selection:
```{r, echo=F}
renderText({
  input$stateFilter
})
```
